Spatio-temporal estimates of risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2022-03-13 src/docs_amazon-poster/amazon-poster.Rmd
Poster progress including models, logos, consulting Pinar on headline #77

---
main_topsize: 0.2
main_bottomsize: 0.1
poster_height: "48in"
poster_width: "36in"
font_family: "Open Sans"
#ESSENTIALS
title: Spatio-temporal estimates of risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
author:
  - name: '**Adam Howes**'
    affil: 1
    main: true
    twitter: adamhowes
    email: ath19@ic.ac.uk
affiliation:
  - num: 1
    address: Department of Mathematics, Imperial College London
main_findings:
  - "**Large efficiency gains** possible by targeting HIV programming using **risk behaviour**."
# Style & formatting
title_textsize: "60pt"
author_textsize: "1.17em"
authorextra_textsize: "35px"
affiliation_textsize: "25px"
affiliation_textcol: '#00000080'
caption_fontsize: "20pt"
# Main
main_fontfamily: "Open Sans"
# Poster body options
primary_colour: '#38761C'
secondary_colour: '#3b77D8'
accent_colour: "#5d19c4"
body_bgcol: "#ffffff"
body_textsize: "45px"
body_textcol: "#000000"
reference_textsize: "23px"
# Standard options
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    highlight: espresso
    number_sections: true
---

@@

* Adolescent girls and young women (15-29) face higher risk of HIV, and have been identified as a priority population for prevention efforts
* The UNAIDS Global AIDS Strategy recommends differentiating services based on local HIV incidence and individual risk behaviours

@@

1. Fit multinomial model to $k = 1, 2, 3^{+}$
2. Fit logistic regression model $k = 3, 4$
3. Differentiate $k = 3^{+}$ into $k = 3$ and $k = 4$
4. Adjust national-level FSW estimates

>>>>

---
main_topsize: 0.2
main_bottomsize: 0.05
poster_height: "48in"
poster_width: "36in"
font_family: "Open Sans"
#ESSENTIALS
title: Spatio-temporal estimates of risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa
author:
  - name: '**Adam Howes**'
    affil: 1
    main: true
    twitter: adamhowes
    email: ath19@ic.ac.uk
  - name: "Kathryn A. Risher"
    affil: 3
  - name: "Van Kinh Nguyen"
    affil: 3
  - name: "Oliver Stevens"
    affil: 3
  - name: "Katherine M. Jia"
    affil: 4
  - name: "Tim M. Wolock"
    affil: 1
  - name: "Lycias Zembe"
    affil: 5
  - name: "Ian Wanyeki"
    affil: 5
  - name: "Mary Mahy"
    affil: 5
  - name: "Clemens Benedikt"
    affil: 5
  - name: "Seth R. Flaxman"
    affil: 6
  - name: "Jeffrey W. Eaton"
    affil: 2
affiliation:
  - num: 1
    address: Department of Mathematics, Imperial College London
  - num: 2
    address: MRC Centre for Global Infectious Disease Analysis, School of Public Health, Imperial College London
  - num: 3
    address: Department of Medical Social Sciences, Feinberg School of Medicine, Northwestern University
  - num: 4
    address: Harvard T. H. Chan School of Public Health, Harvard University
  - num: 5
    address: Joint United Nations Programme on HIV/AIDS, Geneva, Switzerland
  - num: 6
    address: Department of Computer Science, University of Oxford
main_findings:
  - "Targeting HIV programming based on risk behaviour would **greatly increase** resource allocation efficiency."
logoleft_name: "IMP_ML_W_N.png"
logoright_name: "UNAIDS-reverse-EN.gif"
# Style & formatting
title_textsize: "60px"
author_textsize: "1.17em"
authorextra_textsize: "35px"
affiliation_textsize: "25px"
affiliation_textcol: '#00000080'
caption_fontsize: "20px"
# Main
main_fontfamily: "Open Sans"
# Poster body options
primary_colour: '#38761C'
secondary_colour: '#3b77D8'
accent_colour: "#5d19c4"
body_bgcol: "#ffffff"
body_textsize: "40px"
body_textcol: "#000000"
reference_textsize: "20px"
# Standard options
output: 
  posterdown::posterdown_betterport:
    self_contained: false
    pandoc_args: --mathjax
    highlight: espresso
    number_sections: false
---

@@

* Adolescent girls and young women (AGYW) 15-29 continue to **face higher risk** of HIV, and have been identified as a **priority population** for prevention efforts
* The UNAIDS Global AIDS Strategy **recommends differentiating services** for AGYW geographically based on individual risk behaviours
* We used a spatio-temporal model to estimate the proportion of AGYW in **four behavioural risk categories** in 13 priority countries at a district level in the years 1999-2020

@@

* We used 48 household surveys (including AIS, BAIS, DHS and PHIA) but only 13 included a specific question about paid sex
* For the categories $k \in \{1, 2, 3^{+}\}$ we specified a multinomial logistic regression via the multinomial-Poisson transformation
\begin{align}
    &y_{itak}^\star \sim \text{xPoisson}(\kappa_{itak}), \\
    &\log(\kappa_{itak}) = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{ck} + \phi_{ik} + \gamma_{tk},
\end{align}
where $p_{itak} = \text{softmax}(\kappa_{ita})_k$.

* To differentiate $3^{+}$ we used a logistic regression
\begin{align}
    &y_{ia4}^\star \sim \text{xBinomial} \left( y_{ia3} + y_{ia4}, p_{ia4} / (p_{ia3} + p_{ia4}) \right), \\
    &\text{logit}(p_{ia4} / (p_{ia3} + p_{ia4})) = \beta_0 + \alpha_a + \zeta_c + \phi_i + \beta_\texttt{cfswever}.  
\end{align}
